### 2013-11-01 finalTables.Rmd
restructuring the whole lot. Creative destruction

% Final graphics for the paper

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knit("finalPlots.Rmd")
system("pandoc -s finalPlots.md -o finalPlots.html --toc --number-section")

@@

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#########################################
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
```

# GDP change

```{rattribFinalPlotsGDP}
# valitaan vaan kohdemaat

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gdp.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_gdp.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()
```

![](figure/scatter_gdp.png)

# UNU-Wider Gini

```{rattribFinalPlotsGini}
# UNU-Wider Gini

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, uw_gini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=uw_gini, y=socialBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=uw_gini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, uw_gini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=uw_gini, y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +  
  geom_point(data=t4, aes(x=uw_gini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_gini.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_gini.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()
```

![](figure/scatter_gini.png)

# World Bank - Voice and Accountability

```{rattribFinalPlotsWB}

# World Bank - Voice and Accountability

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=wbgi_vae, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Voice and Accountability Index 2011", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=socialBlame, color=group_general)) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=socialBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=wbgi_vae, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Voice and Accountability Index 2011", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=individualBlame, color=group_general)) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=individualBlame, label=cntry),
            color="Dim Grey", size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_wbgi.pdf", width=14/2.54, height=10/2.54)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

ppi <- 300
png("figure/scatter_wbgi.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=2)
dev.off()

![](figure/scatter_wbgi.png)

```{rattribFinalPlotsx, eval=FALSE}

>>>>

% Final regression ouput tables for the paper

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knit("finalTables.Rmd")
system("pandoc -s finalTables.md -o finalTables.html --toc --number-section")

@@

**In progress..**

See old model outputs [here](file:///home/aurelius/workspace/lits/attrib/attrib_year2013/code/multilevel_models.html)

### 2013-11-01 index.Rmd
restructuring the whole lot. Creative destruction

cd ~/workspace/lits/attrib/attrib_year2013/figures
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/
```

@@

Analytical code is licensed under open [FreeBSD](http://en.wikipedia.org/wiki/BSD_licenses#2-clause_license_.28.22Simplified_BSD_License.22_or_.22FreeBSD_License.22.29)-licence.

@@

## Cleaning the data & missing data

html-ouput                                                    source code
-------------------------------------------------------       -----------------------------
[loading and cleaning](loadClean.html)                        [source](loadClean.Rmd)
[missing data & diagnostics](code/descriptive_analysis.html)  [source](code/descriptive_analysis.Rmd)

@@

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Descriptive analysis](descriptive_analysis.html)         [source](descriptive_analysis.Rmd)
[Graphics in the paper]()                                 [source](descriptive_analysis.Rmd)

@@

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Output tables in html](code/multilevel_models.html)      [source](code/multilevel_models.Rmd)
[Output tables in pdf](code/multilevel_models.pdf)        [source](code/multilevel_models.Rmd)

@@

- [Article draft in .html](article2013.html)
- [Article draft in .pdf](article2013.pdf)
- [Article draft in .epub](article2013.epub)

>>>>

cd ~/workspace/lits/attrib/attrib_year2013/
lftp -u np16003 -e "mput *.html *.Rmd *.pdf *.epub *.docx;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/

cd ~/workspace/lits/attrib/attrib_year2013/figure
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/figure
```

@@

**Analytical code is licensed under open [FreeBSD](http://en.wikipedia.org/wiki/BSD_licenses#2-clause_license_.28.22Simplified_BSD_License.22_or_.22FreeBSD_License.22.29)-licence.**

@@

## Cleaning the data & variable summaries

-------------------
html-ouput                                                    source code
-------------------                                           ---------
[loading, cleaning and summarizing](loadClean.html)           [source](loadClean.Rmd)
-------------------

@@

-------------------
html-ouput                                                source code
-----------------------                                   ---------
[Descriptive analysis](descriptive_analysis.html)         [source](descriptive_analysis.Rmd)

[Graphics in the paper](finalPlots.html)                  [source](finalPlots.Rmd)
-------------------

@@

-------------------
html-ouput                                                source code
-----------------------                                   ---------
[Regression analysis](code/multilevel_models.html)        [source](code/multilevel_models.Rmd)

[Final tables](finalTables.html)                          [source](finalTables.Rmd)
-------------------

- [Final tables as A4 .pdf](finalTables.pdf)

@@

- [Article draft in .html](article2013.html)
- [Article draft in .pdf](article2013.pdf)
- [Article draft in .epub](article2013.epub)
- [Article draft in .docx](article2013.docx)

### 2013-11-01 loadClean.Rmd
restructuring the whole lot. Creative destruction

lits2$income[lits2$q227 == 1:3]  <- 'Low income'
lits2$income[lits2$q227 == 4:7]  <- 'Middle income'
lits2$income[lits2$q227 == 8:10] <-'High income'

@@

lits2$income2 <- factor(recode(lits2$q227, 
                              "1:5='Low'; 
                              6:10='High'; 
                              else=NA"))

lits2$income <- factor(lits2$income2, levels=c("Low","High"))

# median(lits2)
#svyquantile(~q227, d.df, quantile = c(0.25, 0.5, 0.75), ci = TRUE)
library(car)
lits2$q227_rec <- recode(lits2$q227, "-111:0=NA")
###

# $future
###

lits2$future <- factor(recode(lits2$q229, 
                              "1:3='a) low income'; 
                          4:7='b) middle income'; 
                              8:10='c) high income'; 
                              else=NA"))

lits2$q229_rec <- recode(lits2$q229, "-100:0=NA")

lits2$future.diff[lits2$q227_rec > lits2$q229_rec] <- 'worse'
lits2$future.diff[lits2$q227_rec <= lits2$q229_rec] <- 'same or better'
lits2$future.diff <- factor(lits2$future.diff)

# $past
###

lits2$past <- factor(recode(lits2$q228, 
                              "1:3='a) low income'; 
                          4:7='b) middle income'; 
                              8:10='c) high income'; 
                              else=NA"))

lits2$q228_rec <- recode(lits2$q228, "-111:0=NA")

lits2$past.diff[lits2$q227_rec < lits2$q228_rec] <- 'worse'
lits2$past.diff[lits2$q227_rec >= lits2$q228_rec] <- 'same or better'
lits2$past.diff <- factor(lits2$past.diff)

# $age
###

lits2$ageclass <- factor(recode(lits2$q104a_1, 
                              "1:29='29 or younger'; 
                          30:44='30 to 44'; 
                              45:59='45 to 59';
                              60:120='60 and older';
                                else=NA"))

lits2$ageclass <- factor(lits2$ageclass, levels=c("29 or younger","30 to 44","45 to 59","60 and older"))

@@

# $incsour tulonlähde
###

lits2$q226m_txt <- recode(lits2$q226m, 
                          "1='Salary or wages in cash or in kind';
                                2='Income from self-employment';
                          3='Sales or bartering of farm products';
                          4='Pensions';5='Benefits from the state';
                          6='Help from relatives or friends';7='Other'")

lits2$incsour3 <- factor(recode(lits2$q226m_txt, 
                                "c('Benefits from the state',
                                'Help from relatives or friends')='Dependent'
                                ;else='Not.dependent'"))

@@

lits2$edu2 <- factor(recode(lits2$q515, "c(1,2)='no or compulsory';
                           else='higher'"))

#################
# $crise - kriisikokemus
#################
lits2$q801 <- as.factor(str_replace(lits2$q801, "Don't know", "DONT KNOW"))
summary(lits2$q801)
lits2$q801 <- factor(lits2$q801, levels=c("A GREAT DEAL","A FAIR AMOUNT","JUST A LITTLE","NOT AT ALL","DONT KNOW","Refused"))

library(car)
lits2$crise <- recode(lits2$q801, "c('A GREAT DEAL','A FAIR AMOUNT')='Great or fair amount';
                       c('NOT AT ALL','JUST A LITTLE')='Little or not at all';
                       else=NA")

lits2$crise <- factor(lits2$crise, levels=c("Little or not at all",
                                            "Great or fair amount"))
summary(lits2$crise)
###

@@

```{rLoadClean5, eval=TRUE}

## Data for the analysis
df <- subset(lits2, select=c("SerialID","weight","cntry","country0","q309",
                             "q309_rec","sex",
                             "ageclass","age",
                             "future.diff","past.diff",
                             "pov.log.social",
                             "pov.log.individual",
                             "socialism","incsour3",
                             "edu2",
                             "group_analysis",
                             #"group_general","group_fine",
                             "income2",
                             "crise",
                             "q227", # income
                             "q228", # menneisyys
                             "q229", # tulevaisuus
                             "q226m_txt", # tulonlähde
                             "q515", # edu
                             "q801" # crise,
                             ))
# filter out not wanted countries
df <- df[!is.na(df$group_analysis),] # valitaan vaan group1 -muuttujan maat
df$cntry <- factor(df$cntry)
# print data in csv-format

summary(df)

@@

```{rLoadClean6, eval=TRUE}
###

library(reshape2)
library(survey)
d.df <- svydesign(id = ~SerialID, 
                  weights = ~weight, 
                  data = df)

summary309 <- data.frame(prop.table(svytable(~q309 + cntry, d.df), 2) * 100)
summary309 <- summary309[!is.na(summary309$Freq), ]

summary309w <- dcast(summary309, cntry ~ q309, value.var="Freq")
names(summary309w) <- c("cntry","social.blame","individual.blame","individual.fate","social.fate","not.stated","dont.know")

summary309_rec <- data.frame(prop.table(svytable(~q309_rec + cntry, d.df), 2) * 100)
summary309_rec <- summary309_rec[!is.na(summary309_rec$Freq), ]

summary309_recw <- dcast(summary309_rec, cntry ~ q309_rec, value.var="Freq")
names(summary309_recw) <- c("cntry","social.blame","individual.blame","individual.fate","social.fate")

@@

library(ggplot2)
ggplot(datQogSum, aes(x=year,y=value,color=cname)) + 
  geom_point() +
  geom_text(data = datQogSum,
            aes(x=year,y=value,color=cname,label=cname)) +
  facet_wrap(~indicator, scales="free") +
  theme(legend.position="none")

datQogSum.w <- dcast(datQogSum, cname ~ indicator, value.var="value")
datQogSum.w$cname <- recode(datQogSum.w$cname, "'United Kingdom'='Great Britain'")

datQogSum.w$group_fine <- recode(datQogSum.w$cname, "c('Armenia','Azerbaijan','Georgia') = 'Caucasus';
                         c('Russia','Ukraine','Moldova','Belarus')= 'CIS North';
                         c('Kyrgyzstan','Kazakhstan','Tajikistan','Uzbekistan')='Central Asia';
                         c('Estonia','Latvia','Lithuania')='Baltic States';
                         c('Poland','Czech Republic','Slovakia','Hungary','Slovenia',
                         'Romania','Bulgaria')='CEE EU';
                         c('Italy','Germany','Great Britain','Sweden','France')='West Europe';
                         else='other'")
datQogSum.w$group_general <- recode(datQogSum.w$cname,
                       "c('France','Germany','Great Britain',
                             'Italy','Sweden')='Western Europe';
                       c('Czech Republic','Estonia','Hungary','Bulgaria',
                       'Latvia','Lithuania','Poland',
                       'Slovakia','Slovenia','Romania')='CEE';
                       c('Armenia','Azerbaijan','Belarus','Georgia','Kazakhstan',
                       'Kyrgyzstan','Moldova','Tajikistan',
                       'Ukraine','Uzbekistan','Russia')='CIS';else=NA")

df.qog <- datQogSum.w
# underschores into dots for latex...
#names <- names(df.qog)
#library(stringr)
#names <- str_replace_all(names, "_",".")
#names(df.qog) <- names
library(gdata)
df.qog <- rename.vars(df.qog, from="cname", to="cntry")

@@

```{rLoadClean9, eval=FALSE}

>>>>

lits2$income[lits2$q227 >= 1 & lits2$q227 <= 3]  <- 'Low income'
lits2$income[lits2$q227 >= 4 & lits2$q227 <= 7]  <- 'Middle income'
lits2$income[lits2$q227 >= 8] <-'High income'

@@

summary(lits2$income)

lits2$income2[lits2$q227 >= 1 & lits2$q227 <= 5]  <- 'Low'
lits2$income2[lits2$q227 >= 6 & lits2$q227 <= 10]  <- 'High'

lits2$income <- factor(lits2$income2, 
                       levels=c("Low",
                                "High"))

summary(lits2$income2)

# median(lits2)
#svyquantile(~q227, d.df, quantile = c(0.25, 0.5, 0.75), ci = TRUE)
library(car)
lits2$q227_rec <- lits2$q227
lits2$q227_rec[lits2$q227_rec <= 0] <- NA
# $future
###

summary(factor(lits2$q229))

lits2$future[lits2$q229 >= 1 & lits2$q229 <= 3] <- "low income"
lits2$future[lits2$q229 >= 4 & lits2$q229 <= 7] <- "middle income"
lits2$future[lits2$q229 >= 8 & lits2$q229 <= 10] <- "high income"

summary(factor(lits2$future))

lits2$q229_rec <- lits2$q229
lits2$q229_rec[lits2$q229_rec <= 0] <- NA

summary(factor(lits2$q229_rec))

lits2$future.diff[lits2$q227_rec > lits2$q229_rec] <- 'worse'
lits2$future.diff[lits2$q227_rec <= lits2$q229_rec] <- 'same or better'
lits2$future.diff <- factor(lits2$future.diff, levels=c("worse",
                                                        "same or better"))

summary(lits2$future.diff)
# $past
###

summary(factor(lits2$q228))

lits2$past[lits2$q228 >= 1 & lits2$q228 <= 3] <- "low income"
lits2$past[lits2$q228 >= 4 & lits2$q228 <= 7] <- "middle income"
lits2$past[lits2$q228 >= 8 & lits2$q228 <= 10] <- "high income"

summary(factor(lits2$past))

lits2$q228_rec <- lits2$q228
lits2$q228_rec[lits2$q228_rec <= 0] <- NA

summary(factor(lits2$q228_rec))

lits2$past.diff[lits2$q227_rec < lits2$q228_rec] <- 'worse'
lits2$past.diff[lits2$q227_rec >= lits2$q228_rec] <- 'same or better'
lits2$past.diff <- factor(lits2$past.diff, levels=c("worse",
                                                    "same or better"))
# $age
###

lits2$ageclass[lits2$q104a_1 <= 29] <- '29 or younger'
lits2$ageclass[lits2$q104a_1 >= 30 & lits2$q104a_1 <= 44] <- '30 to 44'
lits2$ageclass[lits2$q104a_1 >= 45 & lits2$q104a_1 <= 59] <- '45 to 59'
lits2$ageclass[lits2$q104a_1 >= 60 & lits2$q104a_1 <= 120] <- '60 and older'

lits2$ageclass <- factor(lits2$ageclass, 
                         levels=c("29 or younger",
                                  "30 to 44",
                                  "45 to 59",
                                  "60 and older"))

summary(lits2$ageclass)

@@

# $incsour tulonlähde
###
summary(factor(lits2$q226m))

lits2$incsour3[lits2$q226m == 5 | lits2$q226m == 6] <- "dependent"
lits2$incsour3[lits2$q226m > 0 & lits2$q226m < 5 | lits2$q226m > 6 ] <- "notDependent"

lits2$incsour3 <- factor(lits2$incsour3, 
                         levels=c("dependent",
                                  "notDependent"))
summary(lits2$incsour3)
###

@@

summary(factor(lits2$q515))

lits2$edu2[lits2$q515 == 1 | lits2$q515 == 2]  <- "no or compulsory"
lits2$edu2[lits2$q515 >= 3]  <- "higher"

lits2$edu2 <- factor(lits2$edu2,
                     levels=c("no or compulsory",
                              "higher"))

summary(lits2$edu2)
#################
# $crise - kriisikokemus
#################
library(stringr)
lits2$q801 <- as.factor(str_replace(lits2$q801, "Don't know", "DONT KNOW"))

summary(lits2$q801)

lits2$q801 <- factor(lits2$q801, 
                     levels=c("A GREAT DEAL",
                              "A FAIR AMOUNT",
                              "JUST A LITTLE",
                              "NOT AT ALL",
                              "DONT KNOW",
                              "Refused"))

lits2$crise[lits2$q801 %in% c('A GREAT DEAL','A FAIR AMOUNT')] <- 'Great or fair amount'
lits2$crise[lits2$q801 %in% c('NOT AT ALL','JUST A LITTLE')] <- 'Little or not at all'

lits2$crise <- factor(lits2$crise, levels=c("Little or not at all",
                                            "Great or fair amount"))
summary(lits2$crise)
```

@@

```{rLoadClean5, eval=TRUE}
## Data for the analysis
df <- subset(lits2, select=c("SerialID","weight","cntry","country0","q309",
                             "sex",
                             "ageclass","age",
                             "future.diff","past.diff",
                             "pov.log.social",
                             "pov.log.individual",
                             "socialism","incsour3",
                             "edu2",
                             "group_analysis",
                             #"group_general","group_fine",
                             "income2",
                             "crise",
                             "q227", # income
                             "q228", # menneisyys
                             "q229", # tulevaisuus
#                             "q226m_txt", # tulonlähde
                             "q515", # edu
                             "q801", # crise,
                             "poverty"
                             ))
# filter out not wanted countries
df <- df[!is.na(df$group_analysis),] # valitaan vaan group1 -muuttujan maat
df$cntry <- factor(df$cntry)
summary(df)

@@

```{rLoadClean6, eval=TRUE}
###
library(reshape2)
library(survey)
d.df <- svydesign(id = ~SerialID, 
                  weights = ~weight, 
                  data = df)

summary309 <- data.frame(prop.table(svytable(~q309 + 
                                               cntry, d.df), 
                                    2) * 100)

summary309 <- summary309[!is.na(summary309$Freq), ]
summary309w <- dcast(summary309, 
                     cntry ~ q309, 
                     value.var="Freq")
names(summary309w) <- c("cntry","socialBlame",
                        "individualBlame","individualFate",
                        "socialFate","not.stated","dont.know")

summaryPoverty <- data.frame(prop.table(svytable(~poverty + 
                                                   cntry, d.df), 
                                        2) * 100)
summaryPoverty <- summaryPoverty[!is.na(summaryPoverty$Freq), ]

summaryPovertyw <- dcast(summaryPoverty, cntry ~ poverty, value.var="Freq")
names(summaryPovertyw) <- c("cntry","socialBlame","individualBlame","individualFate","socialFate")

@@

library(ggplot2)
ggplot(datQogSum, aes(x=year,y=value,color=cname)) + 
  geom_point(size=4) +
  geom_text(data = datQogSum,
            aes(x=year,y=value,
                color=cname,
                label=cname),
            size=3.5) +
  facet_wrap(~indicator, scales="free") +
  theme(legend.position="none")

datQogSum.w <- dcast(datQogSum, 
                     cname ~ indicator, 
                     value.var="value")

datQogSum.w$cname <-  as.character(datQogSum.w$cname)
datQogSum.w$cname[datQogSum.w$cname %in% "United Kingdom"] <- "Great Britain"

datQogSum.w$group_fine[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Georgia')] <- 'Caucasus'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Russia','Ukraine','Moldova','Belarus')] <- 'CIS North'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Kyrgyzstan','Kazakhstan','Tajikistan','Uzbekistan')] <- 'Central Asia'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Estonia','Latvia','Lithuania')] <- 'Baltic States'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Poland','Czech Republic','Slovakia','Hungary',
                                                'Slovenia','Romania','Bulgaria')] <- 'CEE EU'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Italy','Germany','Great Britain','Sweden','France')] <- 'West Europe'

datQogSum.w$group_fine <- factor(datQogSum.w$group_fine)

summary(factor(datQogSum.w$group_fine))

datQogSum.w$group_general[datQogSum.w$cname %in% c('France','Germany',
                                                   'Great Britain','Italy','Sweden')] <- 'Western Europe';
datQogSum.w$group_general[datQogSum.w$cname %in% c('Czech Republic','Estonia',
                                                   'Hungary','Bulgaria',
                                                   'Latvia','Lithuania','Poland',
                                                   'Slovakia','Slovenia','Romania')] <- 'CEE'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Belarus',
                                                   'Georgia','Kazakhstan',
                                                   'Kyrgyzstan','Moldova',
                                                   'Tajikistan','Ukraine',
                                                   'Uzbekistan','Russia')] <- 'CIS'

datQogSum.w$group_general <- factor(datQogSum.w$group_general)
summary(datQogSum.w$group_general)

df.qog <- datQogSum.w
# underschores into dots for latex...
#names <- names(df.qog)
#library(stringr)
#names <- str_replace_all(names, "_",".")
#names(df.qog) <- names
library(gdata)
names(df.qog)[1] <- "cntry"
```

@@

```{rLoadClean9}
